### 2023-12-27 thesis/chapters/01-introduction.tex
Introduction

\chapter{Introduction}
Manufacturing is experiencing a shift in traditional asset operational status evaluation and utilization. The rise of Industry 4.0 means greater automation and robotization of the production halls to achieve optimal usage of available resources. The secondary aspect in the enterprises' endeavor, however not less important, is to keep track of the equipment wear and tear. The corrective action be it repair or replacement should be done on time in response to the key indicators.

@@

This progress report on the master's thesis is organized as follows. In the problem analysis, in section \ref{section:condition-monitoring} we explore the mechanical maintenance approaches and industry standards on common fault identification. Section \ref{section:signal-preprocessing} summarizes filters for signal preprocessing. The \ref{section:feature-engineering} is about measuring vibrations and their transformation into features meaningful in automatic fault pattern recognition. In \ref{section:diagnostics-techniques}, we delve into modes of machinery diagnostics based on obtained relevant indicators, and \ref{section:evaluation-datasets} describes the most common datasets for machinery faults. Chapter \ref{section:design} proposes the preliminary design of the model exploration and deployment phase of the project.

>>>>

\chapter{Introduction}
Manufacturing experiences a shift in traditional asset operational status evaluation and utilization. The rise of Industry 4.0 means greater automation and robotization of the production halls to achieve optimal usage of available resources. The secondary aspect in the enterprises' endeavor, however not less important, is to keep track of the equipment wear and tear. The corrective action be it repair or replacement should be done on time in response to the key indicators.

@@

This progress report on the master's thesis \rom{2} is organized followingly. The problem analysis chapter \ref{chapter:problem-analysis} begins by exploring the mechanical maintenance approaches and industry standards on common fault identification. Vibration monitoring starts with a section on preprocessing that summarizes basic filters. The process of transforming raw samples into features and their meaningful selection is covered in automatic fault pattern recognition with machine learning models trained in offline and online contexts. An overview follows of the most common machinery fault databases.

Chapter \ref{chapter:design} on solution design starts by posing research questions and establishing goals. Then, the MaFaulDa dataset statistical properties and labeling procedure are described on the original samples as well as on extracted attributes. Data rates with feature selection are derived based on the MaFaulDa. In the section about classification models, we compare the performance for various feature sets in the k-nearest neighbors algorithm. Finally, in preparation for the evaluation part, designated machines in the industrial environment are presented alongside the sensor device suitable for their measurement.

### 2023-12-27 thesis/chapters/02-analysis-B-features.tex
Principal components analysis
Increamental learing results with kNN
Introduction

``Negentropy measures the inclination of a system to increase its level of organization''~\cite{avoci_spectral_2020}. The larger \emph{spectral negentropy} (Equation~\ref{equ:spectral-negentropy}) suggests more fault-induced impulses. $E(k, f, \Delta f)$ denotes the squared envelope spectrum (SES) which is an envelope in the Fourier domain: $\mathcal{F}\{ |y(k, f, \Delta f)|^2 \}$.

@@

\section{Feature transformations}
Numerical features from the feature extraction phase have non-normal distributions and span the range of scales. Broad differences among features skew the spread in the particular axis. Inevitably it can degrade the discernment of fault diagnostics models that map input onto smooth function as regression does~\cite{zheng_feature_2018}. The feature scaling, power transform, and principal component analysis modify attribute values to gain more meaningful predictors, but one must be cautious in model interpretation.

@@

\myequations{Feature euclidian norm}
\begin{ceqn}\begin{align}
\widetilde{f} = \sqrt{f_x^2 + f_y^2 + f_z^2}
\label{equ:min-max-scaler}
\end{align}\end{ceqn}

>>>>

``Negentropy measures the inclination of a system to increase its level of organization''~\cite{avoci_spectral_2020}. The larger \emph{spectral negentropy} suggests more fault-induced impulses. $E(k, f, \Delta f)$ denotes the squared envelope spectrum (SES) which is an envelope in the Fourier domain: $\mathcal{F}\{ |y(k, f, \Delta f)|^2 \}$.

@@

\section{Feature transformations} \label{section:feature-selection}
Numerical features from the feature extraction phase have non-normal distributions and span the range of scales. Broad differences among features skew the spread in the particular axis. Inevitably it can degrade the discernment of fault diagnostics models that map input onto smooth function as regression does~\cite{zheng_feature_2018}. The feature scaling, power transform, and principal component analysis modify attribute values to gain more meaningful predictors, but one must be cautious in model interpretation.

@@

\myequations{Feature euclidian norm}
\begin{ceqn}\begin{align}
\widetilde{f} = \sqrt{f_x^2 + f_y^2 + f_z^2}
\end{align}\end{ceqn}
